---
title: "Wine"
author: "Study Group 13"
date: "24/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load the relevant libraries
library(tidyverse)
library(lubridate)
library(mice) 
library(VIM)
library(dplyr)
library(Hmisc)
library(janitor)
library(readxl)
library(skimr)
```

## 1 Background

why are we visualizing this dataset? what do we want to get out of it?

## 2 Load & inspect Data
We would like to inspect the dataset in the following orders:
2.1 missing, empty, and duplicated values;
2.2 data types;
2.3 weird values, errors, and outliers.

```{r load / inspect data, message = FALSE, warning = FALSE}
# 1. Load the data
original_data <- vroom::vroom("winemag-data-130k-v2.csv") %>% 
  clean_names() %>% 
  select(-x1) # Discard an irrelevant column

# Take a look at the raw data
head(original_data)

# Check for missing values
skim(original_data)

describe(original_data) 

# Check for duplicates
get_dupes(original_data)

# Check data types
glimpse(original_data)

# Check for errors and outliers
ggplot(original_data, aes(x = price)) + geom_boxplot()
ggplot(original_data, aes(x = price)) + geom_histogram(binwidth = 20)
ggplot(original_data, aes(x = points)) + geom_boxplot()
```

Through the inspection, we find:

> *Missing, empty, and duplicated values:*
- `country`: 63 blanks, why missing? should we fix it or not? how to fix it?
- `designation`: 
- `region_1`:
- `region_2`:
- `taster_name`:
- `taster_twitter_handle`:
- `variety`:
- No duplicates.

> *data type:*
- `country`: should be a catergorical variable.
- 

> *weird values, errors, and outliers:*
- `price` appears to have an outlier.
- `points` falls in a reasonal range between 80 and 100, which does not need to be further modified.

## 3 Clean data
This section will follow the order of the previous section and aim to fix the flaws to ease the further visualization.

### 3.1 Resolve the missing values 
```{r clean data 1, message = FALSE, warning = FALSE}
# While trying to fix the missing countries with another locator
# We found that all observations missing country values have unique winery values
# List of all wineries for entries with no country.
wineries_na_country <- original_data %>% 
  filter(is.na(country)) %>% 
  summarise(winery) %>% 
  distinct()

# As some of the wineries in the above list have countries in other entries
# We can use the above list to fill the missing countries with the same wineries
# And the missing countries to the remaining incomparable wineries will be manually searched
wineries_countrymatch <- inner_join(original_data, wineries_na_country, by = "winery") %>%
  group_by(winery, country) %>% 
  summarise(country, winery) %>% 
  distinct()

# Load the manually completed list of countries with wineries
wineries_countryfinal <- read.csv("Winery_Country_List.csv", header = TRUE)

# Fill the missing countries with our final list by wineries 
original_data$country[is.na(original_data$country)] <- wineries_countryfinal$country[match(original_data$winery, wineries_countryfinal$winery)][which(is.na(original_data$country))]

# Check the new status of missing values
skim(original_data$country)

```

