---
title: "Data Visualisation - Final Project"
author: "Group 13 - Alessandro Angeletti, Zichen Wang, Johanna Jeffery, Nitya Chopra and Christopher Lewis"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    highlight: breezedark
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
    fontzize: 10 pt
---

```{r, setup, include = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# Load the relevant libraries
library(tidyverse)
library(lubridate)
library(mice) 
library(VIM)
library(dplyr)
library(Hmisc)
library(janitor)
library(readxl)
library(skimr)
library(ggridges)
library(ggplot2)
library(tm)
library(wordcloud)
library(caret)
library(rsample)
library(GGally)
library(purrr)
library(gridExtra)
library(ggpubr)
library(extrafont)
library(fmsb)
library(RColorBrewer)
library(patchwork)
library(tidytext)
#font_import()
loadfonts(device = "pdf")
```

# Background

> Wine appears in our everyday life, so do the questions arising with it: 
- what wine should I choose for a date/friend reunion? 
- what wine should I pick from the duty free shops at airports? 
- Should I base my purchase decision on price or other things, like country origin or year? 
- ...
- *What should I do if I am not a master of wine?*
>
> To solve this daily question, we decide to pull our data analytics skill set. Using the wine dataset from [Kaggle](https://www.kaggle.com/zynicide/wine-reviews/) with 130k wine ratings, we aim to establish a quick understanding of the essence of pricing and rating of wine. By the end, we will be able to grasp the general picture of wine around the globe, the basics of wine pricing strategy, the key metrics that make a wine good, and a final list of wine recommendation. We invite you to take a short journey through a series of visualizations of our findings with us. 

# Load & inspect Data

> We would like to inspect the dataset in the following orders:

1. Missing, empty, and duplicated values;
1. Data types; and
1. Weird values, errors, and outliers.

```{r load data, message = FALSE, warning = FALSE, echo= FALSE, cache = TRUE}
# 1. Load the data
original_data <- vroom::vroom("winemag-data-130k-v2.csv") %>% 
  clean_names() %>% 
  select(-x1) # Discard an irrelevant column

# Take a look at the raw data
head(original_data)

# Check for missing values
describe(original_data) 

# Check for duplicates
original_data <- original_data[!duplicated(original_data$description), ]

# Check data types
glimpse(original_data)

# Check for errors and outliers
ggplot(original_data, aes(x = price)) +
  geom_boxplot()
ggplot(original_data, aes(x = price)) +
  geom_histogram(binwidth = 20)
ggplot(original_data, aes(x = points)) +
  geom_boxplot()
```

Through the inspection, we find:

> **Missing, empty, and duplicated values:**

- `country`: 63 blanks, this column will be fixed right away due to its importance
- `designation`(wine brand): 37465 blanks
- `price`: 8996 blanks, the blanks will be removed as the column is important but hard to fix
- `province`: 63 blanks
- `region_1`: 21247 blanks, this column will be removed since we do not need it
- `region_2`: 79460 blanks, this column will be removed
- `taster_name`: 26244 blanks, this column will be kept and fixed when needed
- `taster_twitter_handle`: 31213 blanks, this column will be removed
- `variety`: 1 blank, this column will be fixed right away

> **Data type:**

- `country`: should be a categorical variable.
- `points`: should be integer.
- `price`: should be integer.
- `province`: should be a categorical variable.
- `variety`: should be a categorical variable.
- `winery`: should be a categorical variable.
- `taster_name`: should be a categorical variable.

These data types will be fixed whenever needed.

> **Weird values, errors, and outliers:**

- `price` appears to have an outlier.
- `points` falls in a reasonable range between 80 and 100, which does not need to be further modified.
- `description` is very imformative but contains too many different types of values.
- `title` contains numbers(years) and text(vineyard names and wine names).

## Clean Data

> This section will follow the order of the previous section and aim to fix the flaws to ease the further visualization.

### Resolve Missing Values 

```{r, clean data 1, message = FALSE, warning = FALSE, echo = TRUE, cache = TRUE}
# While trying to fix the missing countries with another locator
# We find that all observations missing country values have unique winery values
# List of all wineries for entries with no country.
wineries_na_country <- original_data %>% 
  filter(is.na(country)) %>% 
  summarise(winery) %>% 
  distinct()

# As some of the wineries in the above list have countries in other entries
# We can use the above list to fill the missing countries with the same wineries
# And the missing countries to the remaining incomparable wineries will be manually searched
wineries_countrymatch <- inner_join(original_data, wineries_na_country, by = "winery") %>%
  group_by(winery, country) %>% 
  summarise(country, winery) %>% 
  distinct()

# Load the manually completed list of countries with wineries
wineries_countryfinal <- read.csv("Winery_Country_List.csv", header = TRUE)

# Create a copy of the raw data to clean
clean1 <- original_data

# Fill the missing countries with our final list by wineries 
clean1$country[is.na(clean1$country)] <- wineries_countryfinal$country[match(clean1$winery, wineries_countryfinal$winery)][which(is.na(clean1$country))]
# Clear the R studio environment 
rm(wineries_na_country, wineries_countrymatch, wineries_countryfinal)

# Check the new status of missing values
skim(clean1$country)

# Find out the one missing value in variety(grape type)
variety_na <- clean1 %>% 
  filter(is.na(variety))

# While the other information for this observation is incomparable
# We find a trace of grape type in the description
# The missing grape type is "Petite Sirah"
clean1 <- clean1 %>% 
  mutate(variety = case_when(title == "Carmen 1999  (Maipo Valley)" ~ "Petite Sirah",
                            TRUE ~ variety 
                            ))

# Check for the new status of missing variety
skim(clean1$variety)

```

### Clean Description

```{r clean data 2, message = FALSE, warning = FALSE, echo = TRUE, cache = TRUE}
# Since the description column is really messy
# let's pick a country's description to check
# Pull the description out into a new list
input_words <- clean1$description[clean1$country == "France"]

# Take a grouping of texts and make each element of the resulting vector a document 
input_words <- VectorSource(input_words)
# Take a source object and make it volatile corpora
# A corpus is a collection of documents
# Since the object is volatile, 
# all changes only affect the corresponding R object
input_words <- VCorpus(input_words)

# As we want to extract the descriptive words of wine
# We must get irrelevant words out of the way
irrelevant_words <- c("wine", "winery", "it", "green", "winemaking", "winemark",
                      "without", "alcohol", "although", "across", "age", "almost",
                      "along", "also", "amount", "alongsid", "anoth", "approach",
                      "around", "back", "background", "basic", "barrel", "big",
                      "bit", "blend", "bottl", "bouquet", "cellar", "continu",
                      "core", "cut", "develop", "display", "end", "extra",  "drink",
                      "drinking", "doesnt", "element", "enough", "featur", "feel",
                      "fill", "find", "first", "final", "finish", "focus", "follow",
                      "food", "forward", "frame", "front", "get", "give", "given",
                      "glass", "grape", "here", "hint", "highlight", "hold", "just",
                      "keep", "lack", "last", "layer", "length", "lift", "littl",
                      "made", "make", "mark", "medium", "mix", "month", "mouth",
                      "much", "name", "need", "new", "next", "nose", "note", "now"
                      , "offer", "one", "open", "overal", "pair", "part", "pack",
                      "play", "price", "produc", "provid", "quick", "quit", "palat",
                      "rather", "region",  "remain", "result", "reveal", "right",
                      "round", "run", "select", "seem", "set", "show", "soon",
                      "side", "sip", "small", "slight", "somewhat", "start",
                      "suggest", "suppl", "support", "take", "that", "there"
                      , "though", "time", "togeth", "top", "toward", "two", "turn",
                      "use", "variety", "vine", "vineyard", "vintag", "way",
                      "weight", "will", "winemak", "wineri", "year", "yet",
                      "<e2><80><93>", "<c3><a8>dr", "<c3><a9>" ,"aroma", "flavor",
                      "autolyt", "serious", "reson", "long", "red", "black")

# tm_map allows for the application of transformation functions
# group the function of cleaning the extracted words into a function list
clean_words <- function(inside){
  inside <- tm_map(inside, removePunctuation)
  inside <- tm_map(inside, removeNumbers)
  inside <- tm_map(inside, content_transformer(tolower))
  inside <- tm_map(inside, removeWords, stopwords("en"))
  inside <- tm_map(inside, stemDocument)
  inside <- tm_map(inside, removeWords, irrelevant_words)
  inside <- tm_map(inside, stripWhitespace)
  return(inside)
}

# apply the function list to the extracted words
out_clean_words <- clean_words(input_words)

# create a matrix as a list object
ocw_tdm <- TermDocumentMatrix(out_clean_words)

# select the top 10 frequently appeared words for French wines
top_10_words <- findFreqTerms(ocw_tdm, lowfreq = 3300)
paste0("The Top 10 Words Associated to Wines in ", "France" , " are: ")
print(top_10_words)

# arrange the matrix by rowSums
ocw_m <- as.matrix(ocw_tdm) 
aa <- rowSums(ocw_m)
aa <- sort(aa, decreasing = TRUE)

# turn the sorted matrix into a dataframe for visualiztion
aa_df <- data.frame(words = names(aa),
                    freq = aa)

#turn words into a word cloud plot
word_cloud <- aa_df %>%
  ggplot(aes(x = factor(words, levels = words[order(-freq)]), y = freq)) +
  wordcloud(aa_df$words, aa_df$freq, max.words = 10, color = "red")
```

## Exploratory Data Analysis

```{r clean data 3, message = FALSE, warning = FALSE, echo= FALSE, cache = TRUE}

clean2 <- clean1 %>% 
  # Remove the irrelevant, unfixable columns
  select(-c(region_1, region_2, taster_twitter_handle)) %>% 
  filter(
    !is.na(price),
    !is.na(points),
    !is.na(country)
  ) %>% 
  # Extract values from titles
  mutate(
    company = str_extract(title, '\\D*(?=\\d)'),
    year = as.double(trimws(gsub("[^0-9]", "",  title))),
    year = case_when(
      year < 1934 ~ 0,
      year > 2020 ~ 0,
      TRUE ~ year
      )
     # Missing the info after the numbers
    ) %>% 
  # Modify the data type of country
  mutate(country = as.factor(country))
```

```{r EDA, message = FALSE, warning = FALSE, echo = FALSE, cache = TRUE}
# Scaled Distribution of scores(points)
points_hist <- clean2 %>% 
  ggplot() +
  geom_histogram(aes(x = points), fill = "#49CFAE", binwidth = 1)+
  theme_minimal() +
  labs(y = "",
       x = "Point Score of Wines",
       title = "Scores Follow a Normal Distribution!",
       subtitle = "Distribution of Wine Scores") +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(face = "italic", size = 12),
    axis.text = element_text(face = "bold", size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.title.x = element_text(face = "italic", vjust = -0.5),
    text = element_text(family = "Century Gothic")
  ) +
  xlim(79, 100)

# print the histogram
points_hist

# Scaled Distribution of prices
price_hist <- clean2 %>% 
  filter(price < 155) %>% 
  ggplot() +
  geom_histogram(aes(x = price), fill = "#49CFAE", binwidth = 2) +
  theme_minimal() +
  labs(y = "",
       x = "Prices of Wines",
       title = "Prices of Wines are Right Skewed!",
       subtitle = "Distribution of Wine Prices") +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(face = "italic", size = 12),
    axis.text = element_text(face = "bold", size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.title.x = element_text(face = "italic", vjust = -0.5),
    text = element_text(family = "Century Gothic")
  ) +
  xlim(0, 155)

# print
price_hist

# Scatter plot of Price v Points
price_points <- clean2 %>% 
  filter(price < 155) %>% 
  ggplot(aes(x = price, y = points,)) +
  geom_point(alpha = 0.05, color = "#583d72") + 
  geom_smooth(method = lm,
              formula = y ~ log(x),
              colour = "#f05454",
              size = 2
              ) +
  theme_minimal() +
  labs(title = "Points and Price are Related Logarithmically!",
       subtitle = "Regression of Points Against Price",
       x = "Price",
       y = "Ratings"
       ) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(face = "italic", size = 12),
    axis.text = element_text(face = "bold", size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.title.x = element_text(face = "italic", vjust = -0.5),
    text = element_text(family = "Century Gothic")
  ) 

# print
price_points

# check for the countries with the most entries of wine reviews
ReviewData <- clean2 %>% 
  group_by(country) %>% 
  summarise(tot = n()) %>% 
  arrange(desc(tot)) %>% 
  mutate(percent_of_reviews = round(tot / sum(tot), digits = 4),
         cumsum_reviews = cumsum(percent_of_reviews))

# Barchart of countries with the most entries of wine reviews
dist_plot <- ReviewData %>% 
  head(10) %>%
  mutate(country = as_factor(country)) %>% 
  ggplot(aes(y = reorder(country, tot), x = tot)) +
  geom_col(stat = "identity", 
           fill = "#F14F62") + 
  geom_text(aes(label = sprintf("%.0f%%", 100 * percent_of_reviews), 
                x = tot + 3000), 
            face="bold") +
  theme_minimal() +
  labs(y = "",
       x = "Total Number of Wines",
       title = "US Wines Dominate Dataset!",
       subtitle = "Distribution of Wine Origins for the Top 5 Countries") +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(face = "italic", size = 12),
    axis.text = element_text(face = "bold", size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.title.x = element_text(face = "italic", vjust = -0.5),
    text = element_text(family = "Century Gothic")
  ) 
# print  
dist_plot

# compute the average scores per country
avg_score <- clean2 %>% 
  group_by(country) %>%
  summarise(
    avg_score = mean(points),
    count = n()
  ) %>%
  arrange(desc(avg_score)) %>%
  # select the top 10
  head(10)

# Barchart of wine average scores by countries
avg_score_plot <- avg_score %>% 
  ggplot(aes(x = reorder(country, -avg_score), y = avg_score)) + 
  geom_bar(stat = "identity", fill = "#F14F62") + 
  coord_cartesian(ylim = c(88, 92)) + 
  labs(
    y = "Average Rating",
    x = "",
    title = "England Has The Highest Average Rated Wines!",
    subtitle = "Top 10 Countries by Average Rating"
    ) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(face = "italic", size = 12),
    text = element_text(family = "Century Gothic")
  )
# print
avg_score_plot

# for further visualization
# it's easier to extract the top 10 countries with the most origins of wines,
# create a list, then compare it back to the main dataset
select_c <- c("Engalnd",
              "Austria",
              "Germany",
              "Canada",
              "Hungary",
              "France",
              "Italy",
              "Australia",
              "US",
              "Israel")

# select the two most notable countries into another list
selection_of_countries = c("Germany", "Austria")

# Boxplot of top 10 countries with wine ratings
score_by_country <- clean2 %>% 
  filter(country %in% select_c) %>% 
  mutate(options = ifelse(country %in% selection_of_countries, T, F)) %>% 
  ggplot(aes(x = points, 
             y = reorder(country, points, FUN = median), 
             color = options)) +
  geom_boxplot() +
  scale_color_manual(values = c("#000000", "#49CFAE")) +
  theme_minimal() +
  stat_summary(geom = "point",
               color = "#F14F62") +
  labs(
    y = "",
    x = "Points",
    title = "Novices, stick to German and Austrian Wines!",
    subtitle = "Distribution of Scores by Country"
  ) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(face = "italic", size = 12),
    legend.position = "none",
    axis.text = element_text(face = "bold", size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.title.x = element_text(face = "italic", vjust = -0.5),
    text = element_text(family = "Century Gothic")
  )

# print  
score_by_country

# extract the countries among the top 10 for better wine decisions
# and the countries for relatively riskier wine decisions
down_side = c("Israel", "France", "US", "Australia")
up_side = c("Italy", "Germany", "Austria", "Hungary", "Canada")

# Violin Plot of countries among the 10 for better wine preferences
violin_plot <- clean2 %>% 
  filter(country %in% select_c) %>%
  mutate(colouring = ifelse(country %in% up_side, T, F)) %>%
  ggplot(aes(x = points, y = reorder(country, colouring), fill = colouring)) +
  geom_density_ridges(alpha = 0.75) +
  theme_ridges() + 
  theme(legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        plot.title = element_text(face = "bold", size = 16, vjust = 3),
        plot.subtitle = element_text(face = "italic", size = 12, vjust = 3),
        text = element_text(family = "Century Gothic")
    ) +
  labs(title = "Avoid Picking the Bad Blue Wines!",
       subtitle = "Avoid Downside Tail Risk by Selection Blue Wines",
       x = "Scores",
       y = ""
       ) +
  geom_vline(xintercept = 85, linetype = "dashed", color = "black", size = 1) +
  geom_vline(xintercept = 91, linetype = "dashed", color = "black", size = 1) +
  scale_fill_manual(values = c("#d35d6e", "#61b15a")) +
  geom_text(x = 82, y = .7, label = "Bottom 16%", size = 4.5, color = "grey50", color = "grey50") +
  geom_text(x = 93, y = .7, label = "Top 16%", size = 4.5, color = "grey50", color = "grey50")
# print
violin_plot 

# rank the countries by average price
# select only the countries with more than 50 reviews
avg_price_all <- clean2 %>% 
  group_by(country) %>%
  summarise(
    avg_price = mean(price),
    count = n()
  ) %>%
  filter(count > 50) %>% 
  arrange(desc(avg_price))

# create a data frame of price range
df <- clean2 %>% 
  filter(!is.na(price))%>% 
  select(price) %>%  
  table()
df1 <- prop.table(df) 

# select a price cutoff at $155
paste0("Portion of wines under $155: ", round(cumsum(df1)['155'] * 100, 0), "%")
```

# Data Analysis - Predicting Price and Score

> After cleaning the data, we would like to create regression models to help us predict the price and score. In doing so, we would gain more knowledge in understanding what the key metrics that influence a wine's price and rating are.

## Regression - Scores

### OLS

```{r OLS Scores, message = FALSE, warning = FALSE, echo= FALSE, cache = TRUE}
dataAnalysis <- clean2 %>% 
  # use the cutoff
  filter(price < 156,
         country %in% c("Spain", "Italy", "Portugal", "US", "France"),
         year > 0
         ) %>% 
    
  # change the data type
  mutate(
    points = as.integer(points),
    price = as.integer(price),
    winery = as.factor(winery),
    province = as.factor(province),
    variety = as.factor(variety),
    taster_name = as.factor(taster_name)
  )

# look at the explanatory power of price to score
ols_model <- lm(points ~ price, dataAnalysis)
#summary(ols_model)

# R-Squared of: 0.2934

# look at the explanatory power of price and log(price) to score
ols_model2 <- lm(points ~ price + log(price), dataAnalysis)
#summary(ols_model2)

# R-Squared of: 0.3498 

# compare the previous two models
anova(ols_model, ols_model2)
# Our model improved as the p-value (2.2e-16) is far below alpha
# log(price) is proved to be an influential metric of wine scores

# test the explanatory power of power to score
ols_model3 <- lm(points ~ price + log(price) + country, dataAnalysis)
#summary(ols_model3)

# R-Squared of: 0.3616
# country is also influential

# test the explanatory power of year to score
ols_model4 <- lm(points ~ price + log(price) + country + year, dataAnalysis)
#summary(ols_model4)

# test the explanatory power without score
ols_model4b <- lm(points ~ log(price) + country + year, dataAnalysis)
#summary(ols_model4b)

# R-Squared of: 0.3733
# R-Squared of: 0.3723
# price seems to be not influential

# test the explanatory power of taster_name to score
ols_model5 <- lm(points ~ log(price) + country + year + taster_name, dataAnalysis)
#summary(ols_model5)

# R-Squared of: 0.4031 

# test the explanatory power of variety instead of taster_name to score
ols_model6 <- lm(points ~ log(price) + country + year + variety, dataAnalysis)
#summary(ols_model6)

# R-squared of: 0.3958

# test the explanatory power of variet-year interaction instead of year and variety alone to score
ols_model6b <- lm(points ~ price + log(price) + country + year*variety, dataAnalysis)
#summary(ols_model6b)

# R-squared of: 0.3996

# test the explanatory power of province instead of variety to score
ols_model7 <- lm(points ~ price + log(price) + country + year + province, dataAnalysis)
#summary(ols_model7)

# R-squared of: 0.3954 

# test the explanatory power of province-year interaction instead of province alone to score
ols_model8 <- lm(points ~ price + log(price) + country + year*province, dataAnalysis)
#summary(ols_model8)

# R-squared of: 0.4031 

# pick the influential metrics so far
ols_model9 <- lm(points ~ price + log(price) + country + year*province + year*variety, dataAnalysis)
#summary(ols_model9)

# R-squared of: 0.4237 

# pick the influential metrics without price
ols_model10 <- lm(points ~ log(price) + country + year*province + year*variety, dataAnalysis)
#summary(ols_model10)
# R-squared of: 0.4234

# compare the last four models
anova(ols_model7, ols_model8, ols_model9, ols_model10)
# Our model improved as the p-value (2.2e-16) is far below alpha

# Ols_model9 is chosen as the R-squared is the highest
```

> After testing regression models with different variables, we find that price, log(price), country, the year-province interaction, and year-variety interaction are the influential metrics of wine ratings.

### K-Fold

```{r K-Fold Score, message = FALSE, warning = FALSE, echo = TRUE, cache = TRUE}
control <- trainControl (
    method = "cv",
    number = 5,
    verboseIter = TRUE)

# Commented due to vector size error...

# We are going to train the model and report the results using k-fold cross validation
# plsFit <- train(
#   points ~ log(price) + country + year*province + year*variety,
#   dataAnalysis,
#   method = "lm",
#   trControl = control
#   )
# 
# print(plsFit)

# RMSE     Rsquared  MAE    
# 2.54     0.3368    1.87
```

### LASSO

```{r LASSO Scores, message = FALSE, warning = FALSE, echo= TRUE, cache = TRUE}

set.seed(1234)
# we will look for the optimal lambda in this sequence 
# (we will try 100 different lambdas)
lambda_seq <- seq(0, 0.01, length = 100)
# lasso regression using k-fold cross validation to select the best lambda

# split the data in testing and training
train_test_split <- initial_split(dataAnalysis, prop = 0.01)
training <- training(train_test_split)
testing <- testing(train_test_split)

lasso <- train(
 points ~ log(price) + country + year*province + year*variety,
 data = training,
 method = "glmnet",
  preProc = c("center", "scale"),
  trControl = control,
  tuneGrid = expand.grid(alpha = 1, lambda = lambda_seq)
  )

# Model coefficients
coef(lasso$finalModel, lasso$bestTune$lambda)

# Best lambda
lasso$bestTune$lambda

predictions <- predict(lasso, testing)

# Model prediction performance
data.frame(
  RMSE = RMSE(predictions, testing$points),
  Rsquare = R2(predictions, testing$points)
)
```

## Regression for Price

### OLS

```{r OLS Price, message = FALSE, warning = FALSE, echo= FALSE, cache = TRUE, cache = TRUE}

dataAnalysis_2 <- clean2 %>% 
  filter(price < 156,
         country %in% c("Spain", "Italy", "Portugal", "US"),
         year > 0
         ) %>% 
  mutate(
    points = as.integer(points),
    price = as.integer(price),
    winery = as.factor(winery),
    province = as.factor(province),
    variety = as.factor(variety),
    taster_name = as.factor(taster_name),
    year = as.integer(year)
  )

ols_model_1 <- lm(price ~ points, dataAnalysis_2)
#summary(ols_model_1)

# R-Squared of: 0.2822

ols_model_2 <- lm(price ~ log(points), dataAnalysis_2)
#summary(ols_model_2)

# R-Squared of: 0.2779

ols_model_3 <- lm(price ~ I(points^2), dataAnalysis_2)
#summary(ols_model_3)

# R-Squared of: 0.2863

ols_model_4 <- lm(price ~ I(points^2) + province, dataAnalysis_2)
#summary(ols_model_4)

# Adjusted R-Squared of: 0.3387

ols_model_5 <- lm(price ~ I(points^2) + year, dataAnalysis_2)
#summary(ols_model_5)

# Adjusted R-Squared of: 0.3014

ols_model_6 <- lm(price ~ I(points^2) + variety, dataAnalysis_2)
#summary(ols_model_6)

# Adjusted R-Squared of: 0.4312

ols_model_7 <- lm(price ~ I(points^2) + taster_name, dataAnalysis_2)
#summary(ols_model_7)

# Adjusted R-Squared of: 0.3332

ols_model_8 <- lm(price ~ I(points^2) + variety + province, dataAnalysis_2)
#summary(ols_model_8)

# Adjusted R-Squared of: 0.4441

ols_model_9 <- lm(price ~ I(points^2) + variety + province + year, dataAnalysis_2)
#summary(ols_model_9)

# Adjusted R-Squared of: 0.4459

ols_model_10 <- lm(price ~ I(points^2) + variety*year + province*year, dataAnalysis_2)
#summary(ols_model_10)

# Adjusted R-Squared of: 0.453 

anova(ols_model_6, ols_model_8, ols_model_9, ols_model_10)
# Our model improved as the p-value (2.2e-16) is far below alpha

# Ols_model_10 is chosen as the R-squared is the highest
```

> After testing regression models with different variables, we find that the square of ratings, the year-province interaction, and year-variety interaction are the influential metrics of wine price.

### K-Fold

```{r K-Fold Price, message = FALSE, warning = FALSE, echo= TRUE, cache = TRUE}
control <- trainControl (
    method = "cv",
    number = 5,
    verboseIter = TRUE)

# Commented due to vector size error...

# We are going to train the model and report the results using k-fold cross validation
# plsFit_2 <- train(
#   price ~ I(points^2) + variety*year + province*year,
#   dataAnalysis_2,
#   method = "lm",
#   trControl = control
#   )
# 
# print(plsFit_2)

# Adjusted R-squared: 0.4392636
```

### LASSO

```{r LASSO Price, message = FALSE, warning = FALSE, echo= TRUE, cache = TRUE}
set.seed(1234)

# we will look for the optimal lambda in this sequence 
# (we will try 100 different lambdas)
lambda_seq <- seq(0, 0.01, length = 100)
# lasso regression using k-fold cross validation to select the best lambda

# split the data in testing and training
train_test_split_2 <- initial_split(dataAnalysis_2, prop = 0.01)
training_2 <- training(train_test_split_2)
testing_2 <- testing(train_test_split_2)

lasso <- train(
 price ~ I(points^2) + variety*year + province*year,
 data = training_2,
 method = "glmnet",
  preProc = c("center", "scale"),
  trControl = control,
  tuneGrid = expand.grid(alpha = 1, lambda = lambda_seq)
  )

# Model coefficients
coef(lasso$finalModel, lasso$bestTune$lambda)

# Best lambda
lasso$bestTune$lambda

predictions <- predict(lasso,testing_2)

# Model prediction performance
data.frame(
  RMSE = RMSE(predictions, testing_2$points),
  Rsquare = R2(predictions, testing_2$points)
)
```

# Wine Description Analysis

## Build Variables

```{r build variables, message = FALSE, warning = FALSE, echo = TRUE, cache = TRUE}
# Using the word clouds plotted earlier, and consulting websites on wine tasting,
# let's create some key characteristics to comment on for wines, and develop
# lists with other words that are similar.
# We will use these to gain insight into the information contained in the description column

citrus_list <- c("citrus", "orange", "lemon", "lime", "citric", "grapefruit", "mandarin",
                 "yuzu", "rind", "pith", "tangerine", "zesty", "zestiness", "citrusy", "tangy")
berry_list <- c("berry", "berri", "cherry", "cherri", "blackberry", "raspberry", "strawberry",
                "berries", "gooseberry", "cranberry", "blueberry", "raisins", "currant",
                "blackcurrant", "redcurrant", "mulberry")
fruity_list <- c("fruit", "peach", "plum", "pear", "apple", "tropical", "pineapple", "mango",
                 "fruity","fruits", "guava", "apricot", "melon", "nectarine", "fig", "kiwi",
                 "fruitiness", "jam", "jammy", "banana", "fig", "passionfruit",
                 "passion fruit", "pomegranate")
sweet_list <- c("sweet", "vanilla", "chocolate", "honey", "cinnamon", "caramel", "toffee",
                "sugary", "sugar", "maple syrup", "butterscotch", "cocoa", "honeysuckle")
spice_list <- c("spice", "spicy", "pepper", "cumin", "anise", "clove", "nutmeg", "juniper",
                "clove", "cardamom", "peppery", "chilli", "bergamot", "capsicum")
herby_list <- c("herb", "herby", "herbal", "thyme", "sage", "basil", "parsley", "dill",
                "rosemary", "oregano", "herbs", "sorrel", "lavendar", "jasmine", "pine")
nutty_list <- c("walnut", "almond", "hazelnut", "cashew", "macadamia", "peanut", "nutmeg",
                "nutty", "walnuts", "almonds", "hazelnuts", "cashews", "macadamias", "peanuts")
crisp_list <- c("crisp", "tart", "acidic", "dry", "acidity")
fresh_list <- c("fresh", "light", "refreshing", "clean")
coffee_list <- c("coffee", "mocha", "espresso")
rich_list <- c("oaky", "rich", "cedar", "creamy", "woody", "leather", "toasty", "smoky",
               "mature", "butter", "buttery", "biscuit", "sandalwood")


# Check for duplicates and remove
clean2 <- clean2[!duplicated(clean2$description), ]

# Create unique ID for each wine, then tokenize description variable so we can analyze each word
word_description <- clean2 %>%
  dplyr::mutate(ID = row_number()) %>% 
  unnest_tokens(word, description)

# Create new variables that can flag when certain words appear in the description
characteristics <- word_description %>%
  mutate(
    citrus = case_when(
      word %in% citrus_list ~ 1,
      TRUE ~ 0),
    
    berry = case_when(
      word %in% berry_list ~ 1,
      TRUE ~ 0),
    
    fruity = case_when(
      word %in% fruity_list ~ 1,
      TRUE ~ 0),
    
    sweet = case_when(
      word %in% sweet_list ~ 1,
      TRUE ~ 0),
    
    spice = case_when(
      word %in% spice_list ~ 1,
      TRUE ~ 0),
    
    herby = case_when(
      word %in% herby_list ~ 1,
      TRUE ~ 0),
    
    nutty = case_when(
      word %in% nutty_list ~ 1,
      TRUE ~ 0),
    
    crisp = case_when(
      word %in% crisp_list ~ 1,
      TRUE ~ 0),
    
    fresh = case_when(
      word %in% fresh_list ~ 1,
      TRUE ~ 0),
    
    coffee = case_when(
      word %in% coffee_list ~ 1,
      TRUE ~ 0),
    
    rich = case_when(
      word %in% rich_list ~ 1,
      TRUE ~ 0))
```

## Develop Characteristics

> Now that we have our variables for different wine characteristics, let's look at cleaning the 'variety' variable so that we can analyse the prominent characteristics of each wine type.

```{r develope characteristics, message = FALSE, warning = FALSE, echo= FALSE, cache = TRUE}
# Let's inspect the variety variable
variety_cleaning <- clean2 %>%
  group_by(variety) %>% 
  count() %>% 
  arrange(desc(n))

# There are 695 rows of variety
# These varieties are too granular, 
# so let's group some of them together
rm(variety_cleaning)

# Refer to wine classifications from 
# https://winefolly.com/deep-dive/different-types-of-wine/ , 
# let's clean the 'variety' into bigger aggregate groupings
dry_white_list <- c("Chardonnay", "Sauvignon Blanc", "Pinot Grigio", "Muscadet",
                    "Silvaner", "Pinot Blanc", "White Blend", "Grüner Veltliner",
                    "Portuguese White")
sweet_white_list <- c("Muscat", "Riesling", "Chenin", "Vouvray")
sparkling_list <- c("Champagne Blend", "Prosecco", "Cava", "Sparkling Blend")
rose_list <- c("Rosé")
dry_red_list <- c("Rioja", "Malbec", "Monastrell", "Shiraz", "Merlot",
                  "Cabernet Sauvignon", "Red Blend", "Zinfandel", "Pinot Noir",
                  "Syrah", "Bordeaux-style Red Blend", "Sangiovese", "Nebbiolo",
                  "Portuguese Red", "Tempranillo", "Cabernet Franc")

# We need to aggregate these new variables for each individual wine
# (the data frame is still split by each word in the description variable)
char_var1 <- characteristics %>%
  group_by(ID) %>%
  summarise(country, 
            variety, 
            points = mean(points), 
            price = mean(price), 
            citrus = sum(citrus),
            berry = sum(berry),
            fruity = sum(fruity),
            sweet = sum(sweet),
            spice = sum(spice),
            herby = sum(herby),
            nutty = sum(nutty),
            crisp = sum(crisp),
            fresh = sum(fresh),
            coffee = sum(coffee),
            rich = sum(rich)) %>% 
  # remove duplicates
  distinct()

# Turn the mass varieties into categories we created
char_var2 <- char_var1 %>% 
  mutate(wine_type = case_when(
    variety %in% dry_white_list ~ "Dry White",
    variety %in% sweet_white_list ~ "Sweet White",
    variety %in% sparkling_list ~ "Sparkling Wine",
    variety %in% rose_list ~ "Rosé",
    variety %in% dry_red_list ~ "Dry Red",
    TRUE ~ "NA"
  )) %>% 
  select(-ID)

# join the scores of characteristics from citrus package
# clean the table
char_var3 <- char_var2 %>%
  mutate(wine_type = factor(wine_type, 
                            levels = c("Dry Red", "Dry White",
                                       "Sweet White", "Rosé", 
                                       "Sparkling Wine"))) %>% 
  pivot_longer(citrus:rich, 
               names_to = "characteristic", 
               values_to = "score" )

char_var4 <- char_var3 %>%
  filter(wine_type != "NA") %>%
  filter(characteristic != c("nutty","rich")) %>% 
  group_by(wine_type, characteristic) %>% 
  summarise(characteristic, 
            avg_characteristic = mean(score)) %>% 
  distinct()

plot1 <- char_var4 %>% 
  ggplot(aes(x = avg_characteristic, 
             y = characteristic)) +
  geom_col() +
  facet_grid(~wine_type) +
  labs(title = "Pick The Wine With Your Prefered Characteristics",
       subtitle = "Charateristics Scores by Wine Type",
       y = NULL,
       x = NULL) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(face = "italic", size = 12),
    axis.text = element_text(size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    text = element_text(family = "Century Gothic"))
  
plot1
```

## Radar Plots

> Radar plots might be better to visualise these characteristics and compare between wine types. Let's create these below

```{r radar plots, message = FALSE, warning = FALSE, echo= FALSE, cache = TRUE}
char_var5 <- char_var4 %>% 
  pivot_wider(names_from = characteristic, 
              values_from = avg_characteristic)

# Dry Red
char_var_dryred <- char_var5 %>% 
  filter(wine_type == "Dry Red") %>% 
  select(-wine_type, -rich)

char_var_dryred <- char_var_dryred[2:9]

char_var_dryred <- rbind(rep(1.5, 8), 
                         rep(0, 8), 
                         char_var_dryred)

p1 <- radarchart(char_var_dryred, axistype = 1, 
 
    # Custom polygon
    pcol = rgb(0.6, 0, 0.4, 0.9), 
    pfcol = rgb(0.6, 0.2, 0.4, 0.5), 
    plwd = 4, 
    seg = 3,
 
    # Custom the grid
    cglcol = "grey", 
    cglty = 1, 
    axislabcol = "grey30", 
    caxislabels = seq(0, 2, 0.5), 
    cglwd = 0.8,
 
    # Custom labels
    vlcex = 0.8, title = "Dry Red",
    
    # Custom caxislabels
    calcex = 0.7 
    )

# Dry White
char_var_drywhite<- char_var5 %>% 
  filter(wine_type == "Dry White") %>% 
  select(-wine_type, -rich)
  
char_var_drywhite <- char_var_drywhite[2:9]

char_var_drywhite <- rbind(rep(1.5, 8), 
                           rep(0, 8), 
                           char_var_drywhite)

p2 <- radarchart(char_var_drywhite, axistype = 1, 
 
    # Custom polygon
    pcol = rgb(1, 0.8, 0.2, 0.7), 
    pfcol = rgb(1, 1, 0.6, 0.4), 
    plwd = 4 , 
    seg = 3,
 
    # Custom the grid
    cglcol = "grey", 
    cglty = 1, 
    axislabcol = "grey30", 
    caxislabels = seq(0, 2, 0.5), 
    cglwd = 0.8,
 
    # Custom labels
    vlcex = 0.8, 
    title = "Dry White",
    
    # Custom caxislabels
    calcex = 0.7 
    )

# Sweet White
char_var_sweetwhite<- char_var5 %>% 
  filter(wine_type == "Sweet White") %>% 
  select(-wine_type, -rich)
  
char_var_sweetwhite <- char_var_sweetwhite[2:9]

char_var_sweetwhite <- rbind(rep(1.5, 8), 
                             rep(0,8), 
                             char_var_sweetwhite)

p3 <- radarchart(char_var_sweetwhite, axistype = 1, 
 
    # Custom polygon
    pcol = rgb(1, 0.8, 0.2, 0.7), 
    pfcol = rgb(1, 0.9, 0.3, 0.6), 
    plwd = 4, 
    seg = 3,
 
    # Custom the grid
    cglcol = "grey", 
    cglty = 1, 
    axislabcol = "grey30", 
    caxislabels = seq(0, 2, 0.5), 
    cglwd = 0.8,
 
    # Custom labels
    vlcex = 0.8, 
    title = "Sweet White",
    
    # Custom caxislabels
    calcex = 0.7 
    )

# Rosé
char_var_rose <- char_var5 %>% 
  filter(wine_type == "Rosé") %>% 
  select(-wine_type, -rich)
  
char_var_rose <- char_var_rose[2:9]

char_var_rose <- rbind(rep(1.5, 8),
                       rep(0,8),
                       char_var_rose)

p4 <- radarchart(char_var_rose, axistype = 1, 
 
    # Custom polygon
    pcol = rgb(1, 0.6, 0.4, 0.9),
    pfcol = rgb(1, 0.5, 0.4, 0.5), 
    plwd = 4,
    seg = 3, 
 
    # Custom the grid
    cglcol = "grey", 
    cglty = 1, 
    axislabcol = "grey30", 
    caxislabels = seq(0, 2, 0.5), 
    cglwd = 0.8,
 
    # Custom labels
    vlcex = 0.8, 
    title = "Rosé",
    
    # Custom caxislabels
    calcex = 0.7
    )

# Sparkling Wine
char_var_sparkling <- char_var5 %>% 
  filter(wine_type == "Sparkling Wine") %>% 
  select(-wine_type, -rich)
  
char_var_sparkling <- char_var_sparkling[2:9]

char_var_sparkling <- rbind(rep(2, 8),
                            rep(0, 8),
                            char_var_sparkling)

p5 <- radarchart(char_var_sparkling, axistype = 1, 
 
    # Custom polygon
    pcol = rgb(0.7, 0.5, 0.1, 0.9),
    pfcol = rgb(0.7, 0.5, 0.1, 0.4),
    plwd = 4,
    seg = 3, 
 
    # Custom the grid
    cglcol = "grey", 
    cglty = 1, 
    axislabcol = "grey30", 
    caxislabels = seq(0, 2, 0.5), 
    cglwd = 0.8,
 
    # Custom labels
    vlcex = 0.8, title = "Sparkling Wine",
    
    # Custom caxislabels
    calcex = 0.7
    )
```